\documentclass[11pt]{article}
\usepackage[letterpaper,margin=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{microtype}
\usepackage{caption}
\usepackage{enumitem}
\usepackage{float}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.65em}
\setlength{\emergencystretch}{2em}
\definecolor{PlatoBlue}{HTML}{1F4D78}
\hypersetup{colorlinks=true,linkcolor=PlatoBlue,urlcolor=PlatoBlue,citecolor=PlatoBlue}
\captionsetup{font=small,labelfont=bf}
\renewcommand{\arraystretch}{1.18}
\modulolinenumbers[5]
\graphicspath{{../figures/}}


\title{Supplementary Material: Plato-Bio}

\author{Stefan Creadore}

\date{}

\begin{document}

\maketitle

\section*{S1. Reproduction commands}

\begin{verbatim}

.venv/bin/python preprint/experiments/run_globin_structure_benchmark.py
.venv/bin/python preprint/experiments/run_software_validation.py
.venv/bin/python preprint/experiments/build_summary_figures.py

\end{verbatim}

\section*{S2. Structural input inventory}

\resizebox{\textwidth}{!}{%
\begin{tabular}{lrl}
\toprule
File & Bytes & SHA-256 \\
\midrule
1A3N.pdb & 461619 & 1ce17adb5a0a4f986e173aaffa3c3e9910f483f9e32361615a75abb325a1aa7f \\
3RGK.pdb & 147015 & 5fdba6be63ee6d857f3d31cf639452ade4db527c6b14289a13b6a3aa11660f2a \\
AF-P02144-F1.pdb & 102950 & 68dd0c9976dd37bc6787b5b398ddc3ac03b6abdb7cc7025298dd503d8bb3c882 \\
AF-P68871-F1.pdb & 96551 & 37b411f5eaa2ff2e6f51774da344f1bd7b54e78c98ce67d9ffb02d8a3dbdf32a \\
AF-P69905-F1.pdb & 92096 & d9d7ad4607164de17b65767b467d366909d74f96df5176ee368a9a515aaa1911 \\
\bottomrule
\end{tabular}%
}

\section*{S3. Target-level structural results}

\resizebox{\textwidth}{!}{%
\begin{tabular}{lrrrrrrr}
\toprule
Target & Matched & Identity & RMSD (\AA{}) & Median (\AA{}) & Within 2 \AA{} & $\rho$ & P \\
\midrule
hemoglobin\_alpha & 141 & 1.000 & 0.270 & 0.220 & 1.000 & 0.242 & 0.00388 \\
hemoglobin\_beta & 145 & 1.000 & 0.520 & 0.453 & 1.000 & 0.353 & 1.34e-05 \\
myoglobin & 147 & 0.987 & 0.501 & 0.310 & 0.993 & 0.283 & 0.000515 \\
\bottomrule
\end{tabular}%
}

The residue-level CSV contains 433 matched positions.

\section*{S4. Deterministic validation results}

\resizebox{\textwidth}{!}{%
\begin{tabular}{lrrrrrr}
\toprule
Suite & Tests & Passed & Skipped & Failures & Errors & Wall s \\
\midrule
adversarial\_safety & 57 & 56 & 1 & 0 & 0 & 0.89 \\
biology\_domain & 12 & 12 & 0 & 0 & 0 & 0.70 \\
evidence\_and\_citations & 46 & 46 & 0 & 0 & 0 & 1.54 \\
full\_python & 918 & 912 & 6 & 0 & 0 & 67.63 \\
genomics\_adapters & 11 & 11 & 0 & 0 & 0 & 1.15 \\
\bottomrule
\end{tabular}%
}

Targeted suites overlap with the full Python suite. Counts are not additive. Skips remain unvalidated live or platform-specific paths.

\section*{S5. Measurement-repair acceptance criteria}

\begin{itemize}[leftmargin=*]

\item A biology GoldenTask constructs Plato with the biology domain.

\item Method-signal recall is computed from methods.md and included in summary metrics.

\item Evidence JSONL persists drafted Claim rows before EvidenceLink rows.

\item A claim with no supporting source remains in the denominator.

\item A synthetic rigid transformation is recovered by the Kabsch implementation within numerical tolerance.

\end{itemize}

\section*{S6. Interpretation boundary}

The default evaluator executes idea and method stages only. Live LLM, E2B, Modal, hosted PostgreSQL, and authenticated Hugging Face paths require external credentials or services. Same-model reviewer roles are self-critique, not peer review. The autonomous-loop adapters do not establish autonomous scientific improvement.

\section*{S7. bioRxiv packaging notes}

The main manuscript is supplied as one PDF with embedded figures and tables. Supplemental data are separate. No clinical, human-subject, animal, or identifiable-person data are included. Generative AI assistance is disclosed, and the human author remains accountable.

\end{document}
